---
title: "Collab-assignment-4"
author: "Rohan Baghel"
date: '2022-05-20'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  out.width = "80%",
  fig.width = 8, 
  fig.height = 6,
  fig.retina = 3)
set.seed(6)
```

```{r}
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
```

```{r read_data}
La_liga_data <- read.csv("data/laliga_player_stats_english.csv")
```


\section*{Defender}

The motive of this section is to find out the **best defender** in Laliga (Spanish football league), season 2019-2020 according to player stats. We will be analyzing different variables to get the best defender out of the 20 teams. 

```{r}
defender <- La_liga_data %>%
  filter(Position == "Defender") %>%
  select(Team,
         Name,
         Games.played,
         Yellow.Cards,
         Goals.conceded.while.player.on.pitch,
         Interceptions,
         Recoveries,
         Clearances,
         Successful.tackles,
         Unssuccessful.tackles,
         Fouls.committed,
         Successful.duels,
         Duels.lost,
         Successful.aerial.challenges,
         Unsuccessful.aerial.challenges)
```

We will try to find the best defender by going through different levels, the major one being, trying to find the player who has the most recoveries and clearances. 

* Recovery  - A recovery is recorded at the point where the player of the team beginning the possession touches the ball. 

* Clearance - When a player kicks the ball away from the goal they are defending. 

We will only analyze players who have played more than 50% of the games, considering consistency is key factor for a 38 matches long league.

```{r CvsR, fig.align = 'center', fig.cap = "Clearances vs Recoveries"}
defender1 <- defender %>%
  filter(Games.played >= 19)
ggplot(defender1,
       aes(x = Clearances,
           y = Recoveries,
           colour = Team, 
           label = Name)) +
  theme_minimal() +
  geom_text(size = 5) +
  theme_gray(base_size = 15) +
  geom_point() +
  labs(y = "Number of clearances",
       x = "Number of Recoveries",
       title = "Clearances Vs.Recoveries")
  
  
```

From \@ref(fig:CvsR) we can say that **Pique** from **Barcelona** and **Laguardia** from **D. Alaves** have managed to do exceptionally well. Out of the two players, we will try to choose the best defender by bringing in more variables into the picture. 

```{r better}
defender2 <- defender1 %>%
  filter(Name == "Piqué" | Name == "Laguardia") %>%
  mutate(tackles = (Successful.tackles/(Successful.tackles + Unssuccessful.tackles)*100)) %>%
  mutate(duels = (Successful.duels/(Successful.duels + Duels.lost)*100)) %>%
  mutate(aerials = (Successful.aerial.challenges/(Unsuccessful.aerial.challenges +
                                                    Successful.aerial.challenges)*100))

name <- defender2$Name
teams <- defender2$Team
Tackles_success <- defender2$tackles
Duels_success <- defender2$duels
Aerials_success <- defender2$aerials

better <- data.frame(name, teams, goals_conceded, Tackles_success, Duels_success, Aerials_success)

knitr::kable(better, caption = "Comparison of Pique and Laguardia (better)")
  
```
In the table above \@ref(tab:better) we have calculated the percentage of succeessful tackles, duels and Aerial duels won by the each of the defender who came on top in \@ref(fig:CvsR) i.e Pique and Laguardia. Laguardia top the charts between him and Pique in Successful tackles made and Duels won but the difference is bleak. Pique had 20% more Aerial duel success than Laguardia. 

Seems like both of them are are still going to head to head. Now we have to judge them by number of mistakes made by them during the season.

```{r worse}
defender3 <- defender1 %>%
  filter(Name == "Piqué" | Name == "Laguardia")

name <- defender2$Name
teams <- defender2$Team
goals_conceded <- defender2$Goals.conceded.while.player.on.pitch
yellow <- defender3$Yellow.Cards
fouls <- defender3$Fouls.committed

worse <- data.frame(name, goals_conceded, teams, yellow, fouls)

knitr::kable(worse, caption = "Comparison of Pique and Laguardia (worse)")
```

From the table \@ref(tab:worse) we can see Pique has made lesser mistakes in a match the while being on the field as compared to Laguardia. His team conceded lesser goals, he made lesser fouls which resulted him getting penalized less often. We can conclude from our analysis that Pique from Barcelona had the most impact as a defender. On top of that he was also able to contribute in the attack as he scored 4 goals for FC Barcelona.

```{r}
scored <- La_liga_data %>%
  filter(Name == "Piqué") %>%
  select(Name, Team,  Goals.scored)

scored
```



# Position: Forward

The aim of this section is to analyse which player is the best in the *Forward position* in the LaLiga Tournament based on data from 2019-2020.  

```{r Filter-Data}
Forward <- La_liga_data %>%
  filter (Position == "Forward")

Forward <- Forward %>%
  select(Team, Name, Games.played, Yellow.Cards, Goals.scored, Penalties.scored, Successful.tackles, Recoveries, Successful.duels, Assists, Interceptions, Recoveries, Successful.aerial.challenges) %>%
  rename("Games_played" = Games.played,
         "Yellow_cards" = Yellow.Cards,
         "Goals_scored" = Goals.scored,
         "Penalties_scored" = Penalties.scored,
         "Successful_tackles" = Successful.tackles,
         "Successful_duels" = Successful.duels,
         "Successful_aerial_challenges" = Successful.aerial.challenges)
```

Goals Scored, Penalties Scored and Assists account for the most successful outcome given by a player in the Forward position.

```{r Goals-Analysis}
Forward <- Forward %>%
  mutate(goals_per_game = ((Goals_scored + Penalties_scored + Assists)/Games_played)) %>%
  arrange(desc(goals_per_game)) %>%
  mutate(Goal_rank = 1:94)

Forward_Goal <- Forward %>%
  slice_head(n=5) %>%
  select(Team, Name, goals_per_game, Goal_rank) %>%
  kable(caption = "Top 5 forward position players for goals per game") %>%
  kable_styling(position = "center")

Forward_Goal
```

The table \@ref(tab:Goals-Analysis) displays the Name and Team of the top 5 players in the forward position with the highest goals, penalties and assists per game. Messi from Team FC Barcelona holds the first rank in this analysis with an average of 1.55 goals per match, followed by lago Aspas and Suárez.

```{r Success-Scores}
Forward <- Forward %>%
  mutate(success_score = (Successful_tackles + Successful_duels + Successful_aerial_challenges)/Games_played) %>%
  arrange(desc(success_score))  %>%
  mutate(Score_rank = 1:94)

Forward_Score <- Forward  %>%
  slice_head(n=5) %>%
  select(Team, Name, success_score, Score_rank) %>%
  kable(caption = "Top 5 forward position players for Success Score") %>%
  kable_styling(position = "center")

Forward_Score
```
As seen from the table \@ref(tab:Success-Scores), Calleri from team D. Alavés tops the table  with a total success score of 10.02 followed by Enric Gallego and Carrillo The Success score in this table is calculated by adding the successful duels, tackles and aerial challenges by each player divided by the number of games they have played.

```{r goals-v-success, fig.cap = "Goals vs Success score", fig.align='center'}

library(plotly)
p <- ggplot(Forward) + geom_point(aes(x=success_score, y = goals_per_game, hoverinfo = Name)) + labs(x = "Success Score", y = "Goals", title = "Goals vs Success Score")
ggplotly(p)
```
The figure \@ref(fig:goals-v-success) is a scatter plot of all the players' goals and success score per game. The players that occur on the top right corner are so far the top players in our analysis. By hovering the cursor over points we can see that Messi appears to be one of the top players.


```{r Yellow-cards, fig.cap = "Top 20 yellow card players", fig.align='center'}
Forward_yellow <- Forward %>% select(Team, Name, Yellow_cards) %>%
  arrange(desc(Yellow_cards)) %>% slice_head(n=20)

ggplot(Forward_yellow) + geom_col(aes(y=Yellow_cards, x=fct_reorder(Name, Yellow_cards)), fill = "#F6BE00") + 
  theme(axis.text.x = element_text(angle = 45)) +
  labs(title = "Highest yellow card players")
```

The figure \@ref(fig:Yellow-cards) displays the players with the highest number of yellow cards. 

```{r Top}
Forward_top <- Forward %>% anti_join(Forward_yellow) %>%
  mutate(rank = (Goal_rank + Score_rank)/2) %>%
  arrange(rank) %>%
  select(Team, Name) %>% 
  slice_head(n=5)

Forward_top <- Forward_top %>% slice_head(n=5) %>%
  kable(caption = "Top 5 forward position players") %>%
  kable_styling(position = "center")

Forward_top
```

The table \@ref(tab:Top) displays the top 5 forward position players in the LaLiga Tournament according to the 2019-2022 data on the basis of their goals, assists, successful duels and tackles per game and after removing the players with high number of yellow cards. **[Messi from FC Barcelona](images/messi.jpeg)** is at the top of the list followed by M. Gómez, Jorge Molina, Williams and Enric Gallego.\



# Position: Midfielder

### Aim :

* Find out the best attacking midfielders in La Liga and analyze their performance.

* Find out the best defensive midfielders in La Liga and analyze their performance.

Midfielders are the players that are present between the forwards and the defenders. The role of a midfielder is to support both the strikers and the defenders. They act is a link between the attack and defense of a team. The flow of a game is dictated by the midfielders as they are the ones responsible for keeping the ball in possession.

```{r}
Midfielder_data <- La_liga_data %>%
  filter(Position == "Midfielder") %>%
  select(Team,
         Name,
         Position,
         Shirt.number,
         Minutes.played,
         Games.played,
         Passes,
         Tackles,
         Interceptions,
         Recoveries,
         Clearances,
         Successful.tackles,
         Unssuccessful.tackles,
         Fouls.committed,
         Successful.duels,
         Duels.lost,
         Successful.aerial.challenges,
         Unsuccessful.aerial.challenges,
         Successful.dribbles,
         Unsuccessful.dribbles,
         Shots.on.target,
         Shots,
         Assists,
         Goals.scored,
         Penalties.won,
         Fouls.committed,
         Fouls.suffered,
         Yellow.Cards,
         Second.Yellows,
         Red.Cards,
         Fouls.committed.per.card,
         Penalties.given.away) %>%
  arrange(desc(Assists))
```

```{r }
Top_10_Midfielder_Assists <- Midfielder_data %>%
  select(Team,
         Name,
         Shirt.number,
         Games.played,
         Assists) %>%
  arrange(desc(Assists))
```

```{r}
Top_10_Midfielder_Goals <- Midfielder_data %>%
  select(Team,
         Name,
         Shirt.number,
         Games.played,
         Goals.scored) %>%
  arrange(desc(Goals.scored))
```

From the table \@ref(tab:Attack) we can see the attacking performance of midfielders in La Liga. Sarabia of Sevilla FC stands at the top with 12 goals scored and 13 assists with 33 games played. Every other player has fewer assists than him and only J. Morales from Levante UD was able to match his record of 12 goals. 

```{r Attack }
Attack_performance <- inner_join(Top_10_Midfielder_Goals,Top_10_Midfielder_Assists)[1:10,1:6]

kable(Attack_performance, caption = "Best Attacking Midfielders in La Liga (Statistics)") %>%
  kable_material_dark()
```


The figure \@ref(fig:ggAttack) gives a better outlook at the performance of the top midfielders in La Liga. Sarabia and J. Morales standout among their peers as they clearly the leaders in attacking style play, they have scored goals and provided assistance for the benefit of their team. Joaquin from Real Betis is a special case as he is the only midfielder that has provided zero assists but scored 6 goals for his team, earning him a place among the top ten midfielders of La Liga. 


```{r ggAttack,fig.cap = "Best Attacking Midfielders in La Liga" }
ggplot(Attack_performance,
       aes(x = Games.played)) +
  geom_col(aes( y = Goals.scored, color = "Goals scored")) +
  geom_col(aes( y = Assists, color = "Assists")) +
  facet_wrap(~Name, ncol = 5) +
  theme_classic() +
  xlab("Games Played") +
  ylab("Attack Performance") +
  labs(title = "Best Attacking Midfielders in La Liga")
  
```

```{r}
Top_10_Midfielder_Recoveries <- Midfielder_data %>%
  select(Team,
         Name,
         Shirt.number,
         Games.played,
         Recoveries) %>%
  arrange(desc(Recoveries))

```

```{r}
Top_10_Midfielder_Successful_tackles <- Midfielder_data %>%
  select(Team,
         Name,
         Shirt.number,
         Games.played,
         Successful.tackles) %>%
  arrange(desc(Successful.tackles))
```

From the table \@ref(tab:Defense), we see the top defensive midfielders in La Liga. Banega from Sevilla FC tops the table, making 290 recoveries and 50 successful tackles in 32 games. Only Rodrigo from Atlético de Madrid has the most successful tackles than Banega standing at 70. None of the other peers have come closer Rodrigo in their skill of tackling an opponent. 

```{r Defense}

Defence_Performance <- inner_join(Top_10_Midfielder_Recoveries,Top_10_Midfielder_Successful_tackles)[1:10,1:6]

kable(Defence_Performance, caption = "Best Defensive Midfielders in La Liga (Statistics)") %>%
  kable_material_dark()

```


From the figure \@ref(fig:ggDefense) we can see that all the defensive midfielders have been almost at the same skill. The top performers Banega and Rodrigo stand out in their individual departments but are almost at the same level as their peers in La Liga. Banega seems to more of a top performer because he is on the top of table even though has played the fewest games 32, except Rubén Pérez J. who has played 31 and is at the bottom of the table.


```{r ggDefense,fig.cap = "Best Defensive Midfielders in La Liga " }
ggplot(Defence_Performance,
       aes(x = Games.played)) +
  geom_col(aes(y = Recoveries, color = "Recoveries")) +
  geom_col( aes(y = Successful.tackles, color = "Successful tackles")) +
  facet_wrap(~Name, ncol = 5) +
  theme_classic() +
  xlab("Games Played") +
  ylab("Defence Performance") +
  labs(title = "Best Defensive Midfielders in La Liga ") 
```

The best overall performance is given by Parejo of Valencia CF as we can from the table \@ref(tab:best). He has made 270 recoveries, 42 successful tackles, scored 9 goals and made 7 assists. He has been at the third position in both attacking midfielders and defensive midfielders. His performance has been exceptional as midfielder and is quite an ideal candidate for any team.


```{r best}
Best_Midfielder <- inner_join(Defence_Performance,Attack_performance)

kable(Best_Midfielder, caption = "Best Overall Performace") %>%
  kable_material_dark()

```


# Section-4
